%-------------------------
% Resume in Latex
% Author : Ashish Keshan
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{fontawesome}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}
\usepackage{xcolor}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\educationHeading}[7]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
      \text{\small#7}\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/ashishkeshan}{\huge Ashish Keshan}} &  \href{mailto:ashishk1216@gmail.com}{ashishk1216@gmail.com}\\
  \href{https://github.com/ashishkeshan}
  {\color{darkgray}\faGithub~ashishkeshan}~{|}~\href{https://linkedin.com/in/ashishkeshan}{\color{darkgray}\faLinkedinSquare~ashishkeshan} &  (123)-456-7890 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \educationHeading
      {University of Southern California}{Los Angeles, CA}
      {B.S. Computer Science and Business Adminstration;  GPA: 3.81}{Aug. 2015 -- May. 2019}
      {M.S. Computer Science}{Aug. 2018 -- Dec. 2019}
      {Relevant Coursework: Database Systems, Operating Systems, NLP, ML, Analysis of Algorithms}
    % \resumeSubheading
    %   {University of Southern California}{Los Angeles, CA}
    %   {M.S. Computer Science}{Aug. 2018 -- Dec. 2019}
      
    %   {Courses: Natural Language Processing; Machine Learning; Analysis of Algorithms}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {FreeFlows}{Los Angeles, CA}
      {Co-Founder \& CTO}{Apr. 2018 - Present}
      \resumeItemListStart
        \resumeItem{BeatStyle}
          {Designed and developed an iOS music production application that provides users with in-house instrumentals and a recording platform to create and share their music.}
        \resumeItem{Business Responsibilities}
          {Growing the business organization  through marketing as well as working on company financials and legalese.}
        \resumeItem{Metrics}
          {400+ user-created songs, 30,000+ songs and instrumentals played, and 5.0 rating on App Store}
      \resumeItemListEnd
    
    \resumeSubheading
      {Microsoft}{Redmond, WA}
      {Software Engineering Intern - CosmosDB}{Summer 2018}
      \resumeItemListStart
        \resumeItem{Health Monitoring}
          {Wrote automation scripts that continually monitor the health status of database clusters.}
        \resumeItem{Incident Annotation}
          {The scripts fill in clear troubleshooting details which highlight the faulty micro-service and thereby minimize the time to mitigate by about 40\%.}
        \resumeItem{Auto-Mitigation}
          {Resolved 300+ incidents that had quick fixes such as restarting an unresponsive node, thereby preventing an on-call engineer from being paged and reducing human error.}
      \resumeItemListEnd

    \resumeSubheading
      {Yahoo! (Oath:)}{Sunnyvale, CA}
      {Technical Intern - Growth \& Monetization}{Summer 2017}
      \resumeItemListStart
        \resumeItem{Accordion Ad}
          {Devised a new Accordion Ad Layout by implementing custom 3D animations on iOS. The ad unfolds a card ad like an accordion to reveal an image/video as the user scrolls down.}
        \resumeItem{System Development}
          {Changed Yahoo Fantasy Sports iOS ad system from UI Integration to Data Integration to deliver more versatile and extensible ad views.}
        \resumeItem{Tiles Ad}
          {Created a new Tiles ad format for native iOS for use across all Yahoo iOS apps (similar to Instagram Stories Design).}
        \resumeItem{Metrics}
          {Improved click through rate (CTR) of ads on the Fantasy Sports App dashboard by 50\% due to the Accordion format.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Human-Robot Interaction}
      {Built a data pipeline that analyzed videos of children interacting with a robot using OpenCV. Fed results into a neural network to predict with 99\% accuracy whether a child was looking at the robot or away. Technologies: OpenFace, Python}
    \resumeSubItem{Scrabble}
      {Built Scrabble from scratch with a fully functional GUI and computer player. Technologies: C++, Qt}
    \resumeSubItem{Twisted Kicks}
      {Developed the iOS and Android companion apps for the card game. Technologies: Swift, Java }
    \resumeSubItem{KnowItAll}
      {Developed an iOS app with a backend that provides ratings and reviews for all things around or related to USC like restaurants, classes, concerts, etc. Technologies: Swift, Django}
  \resumeSubHeadingListEnd
  
%  ------------INVOLVEMENT--------------------
\section{Involvement}
 \resumeSubHeadingListStart
    \resumeSubItem{Scope}
     {Member of a Computer Science org in which we learn a trending language/framework each semester then apply our learning by creating a project with it. Examples include: React Native, Node.js, and Electron}
     \resumeSubItem{Daily Trojan}
     {Beat writer on USC's student run paper where I covered basketball for a year.}
 \resumeSubHeadingListEnd

\section{Programming Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{Languages}
     {C++, Python, Swift, Objective-C, Java, JavaScript, SQL, NoSQL}
    \resumeSubItem{Technologies}
     {AWS, Firebase, Microsoft SQL Server, Xcode}
 \resumeSubHeadingListEnd

\end{document}
